Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits

### 2022-11-10 04_paper/10_20_draft_newabstract.Rmd
old updates

```{r predicted-diff, fig.cap='Counterfactual estimates of yearly \\textit{Xinhua} mentions and diplomatic missions from Beijing.', fig.show='hold'}
include_graphics(
  here('06_figures/predicted_differences.png')
)
```

>>>>

Figure \@ref(fig:binom-est) shows the point estimates with 95% confidence intervals (CIs) from the four regression specifications enumerated in the methods discussion. The figure contains a left and right panel. On the right, results are shown for models 1 and 2 while on the left, results are shown for models 3 and 4. Recall that the first pair of models uses continuous measures of aid and debt as predictors while the second pair uses binary indicators of whether a developing country is an aid recipient, a debtor, or both of Beijing's. Because of the transformation of the the continuous predictors via the inverse hyperbolic sine, the estimates in the right panel may be interpreted as quasi-elasticities (the percent difference in the response given a percent difference in the predictor). The x-axis in each panel denotes the value of the estimated coefficient, and the y-axis indicates the predictor that corresponds with the point estimate. Red indicates that the response variable is *Xinhua* mentions, and blue indicates that the response variable is diplomatic visits. Zero is indicated along the x-axis via a vertical dotted line. If the 95% CIs of a point estimate contain zero, the estimate falls short of statistical significance at the $p < 0.05$ level.

The results paint a surprising picture of the relationship between Chinese development finance and the outcomes of interest. While H1 (that aid recipients are more likely to received more media coverage targeted at foreign audiences) finds support, H2 (that aid recipients are more likely to host diplomatic missions from Beijing) is not supported. Further, while we fail to reject the null that debtors do not receive any more or less foreign-facing coverage (H3), we unexpectedly reject the null that debtors do not host any more or less diplomatic missions (H4).

In substantive terms, these estimates correspond with an approximately

\begin{table}
\caption{Marginal Effects}
\centering
\begin{tabular}[t]{lcc}
\hline
 & \multicolumn{2}{c}{(\%) Change} \\
 & \textit{Xinhua} Coverage & Diplomatic Visits \\
\hline
Aid & 0.77 & 0.00 \\
Debt & 0.02 & 0.15 \\
\hline
\multicolumn{3}{l}{\rule{0pt}{1em}\textit{Note: }Estimates for Pakistan, 2017.}\\
\end{tabular}
\end{table}
